Graph Neural Networks For Multi-Image Matching

### 2019-11-15 latex/iclr2020/main.tex
Added another citation

\subsection{Multi-image Matching}
Multi-image matching has traditionally been done using optimization based methods minimizing a cycle consistency based loss (see Section \ref{sec:cycconsist}).
\cite{pachauri2013solving} and \cite{arrigoni2017synchronization} use the eigenvectors of the matching matrix to obtain a low dimensional embedding. 
However, the assumption of low Gaussian noise is not realistic.
\cite{zhou2015multi} and \cite{wang2017multi} use more sophisticated optimization techniques on the matching matrix and thus produce more robust solutions.
\cite{leonardos2017distributed} implement a distributed optimization scheme to solve for cycle consistency.
\textcolor{red}{\cite{swoboda2019convex} implement a convex relaxation of the low dimensional embedding problem.}
\textcolor{red}{\cite{shi2016tensor} use tensor power iterations to solve the matching problem, also taking into account the intra-image matching graph.}
As an alternative to optimization based techniques, \cite{tron2017fast} used density based clustering techniques to compute multi-image correspondence.
Moving away from feature matching, \cite{zach2010disambiguating} uses cycle-consistency-like constraints on pose graphs quite effectively.
To the best of our knowledge, we are the first to use graph neural networks for multi-image matching.

@@

There are other methods to build correspondences such as \cite{choy2016universal}, but they only handle two-view constraints and require dense correspondences.
Most similar to our work, \cite{yi2018learning} attempts to improve correspondences by learning match probabilities for two-view RANSAC for greater robustness and speed.
Like us \cite{zhu2017unpaired} use cycle consistency in their loss; however their method is for image generation and is restricted to pairwise cycle consistency.
Our method can be applied to 3 or more images. 
\cite{hartmann2017learned} learns multi-image matching but requires heavy supervision from 3D object reconstructions, which can be difficult or expensive to obtain.
\textcolor{red}{\cite{zhou2015flowweb}, unlike our method, uses dense correspondence, but uses cycle consistency to find semantic matches accross multiple views.}
\textcolor{red}{\cite{suwajanakorn2018discovery} find 3 dimensional latent keypoints, trained using ground truth rotation and translation. However, their method is restricted to a limited number of object categories, which is different from the SfM setting we are considering here.}

>>>>

\subsection{Multi-image Matching}
Multi-image matching has traditionally been done using optimization based methods minimizing a cycle consistency based loss (see Section \ref{sec:cycconsist}).
\cite{pachauri2013solving} and \cite{arrigoni2017synchronization} use the eigenvectors of the matching matrix to obtain a low dimensional embedding. 
However, the assumption of low Gaussian noise is not realistic.
\cite{zhou2015multi} and \cite{wang2017multi} use more sophisticated optimization techniques on the matching matrix and thus produce more robust solutions.
\cite{leonardos2017distributed} implement a distributed optimization scheme to solve for cycle consistency.
\textcolor{red}{\cite{swoboda2019convex} implement a convex relaxation of the low dimensional embedding problem.}
\textcolor{red}{\cite{shi2016tensor} use tensor power iterations to solve the matching problem, also taking into account the intra-image matching graph.}
As an alternative to optimization based techniques, \cite{tron2017fast} used density based clustering techniques to compute multi-image correspondence.
\cite{fathian2019clear} use a similar technique but formulates it as a generalized Rayleigh quotient problem to achieve better results.
Moving away from feature matching, \cite{zach2010disambiguating} uses cycle-consistency-like constraints on pose graphs quite effectively.
To the best of our knowledge, we are the first to use graph neural networks for multi-image matching.

@@

There are other methods to build correspondences such as \cite{choy2016universal}, but they only handle two-view constraints and require dense correspondences.
\textcolor{red}{Most similar to our work, \cite{zhang2019iccv} use graph neural networks to do intra-image feature processing before doing two image inter-image feature similarity. However, their work only trains for pairs of image, while ours is explicitly trained for multi-image matching.}
Also similarly, \cite{yi2018learning} attempts to improve correspondences by learning match probabilities for two-view RANSAC for greater robustness and speed.
Like us \cite{zhu2017unpaired} use cycle consistency in their loss; however their method is for image generation and is restricted to pairwise cycle consistency.
Our method can be applied to 3 or more images. 
\cite{hartmann2017learned} learns multi-image matching but requires heavy supervision from 3D object reconstructions, which can be difficult or expensive to obtain.
\textcolor{red}{\cite{zhou2015flowweb}, unlike our method, uses dense correspondence, but uses cycle consistency to find semantic matches accross multiple views.}
\textcolor{red}{\cite{suwajanakorn2018discovery} find 3 dimensional latent keypoints, trained using ground truth rotation and translation. However, their method is restricted to a limited number of object categories, which is different from the SfM setting we are considering here.}
